---
title: "HW 2- Tara & Darragh"
author: "Darragh"
date: "10/11/2017"
output: html_document
---

x <- 
if(x %% 3 ==0){print(paste(x, "is FIZZ"))}
if(x %% 5 ==0){print(paste(x, "is BUZZ"))}
}else{
  print(paste(x))
  
  
x <- 1

if (x %% 3 == 0){
  print(paste(x, "is FIZZ"))}
if (x %% 5 == 0){
  print(paste(x, "is BUZZ"))}
else{
  print(paste(x,))}



# MAP DATA

library(maps)
library(ggmap)
library(rvest)

# Define webpage
big10 = read_html("http://www.bigten.org/library/stats/fb-confsked.html#standings")

# Get uni names
big10 %>% 
    html_nodes(".b1gfbstats:nth-child(9) td:nth-child(1) , .b1gfbstats:nth-child(6) td:nth-child(1)") %>% 
    html_text() -> uni_name
uni_name = paste(uni_name,"University")

# Find uni locations
uni_coord = data.frame(geocode(uni_name))

# Get win rate
big10 %>% 
    html_nodes("td:nth-child(7)") %>% 
    html_text() -> uni_wp
uni_coord$wp = 100*as.numeric(uni_wp[1:length(uni_name)])

# Get division
uni_coord$conf = rep(c("East Division","West Division"), each = length(uni_name)/2)



# Portfolio Data
library(quantmod)
library(rvest)
sp500 <- read_html("https://en.wikipedia.org/wiki/List_of_S%26P_500_companies")

sp500 %>% 
html_nodes(".text") %>% 
html_text() -> ticker_sp500

SP500_symbol <- ticker_sp500[(1:499)*2+1]
SP500_symbol[SP500_symbol == "BRK.B"] <- "BRK-B"
SP500_symbol[SP500_symbol == "BF.B"] <- "BF-B"


today <- Sys.Date()
three_year_ago <- seq(today, length = 2, by = "-3 year")[2]
getSymbols(SP500_symbol, from = three_year_ago, to = today)



```{r}
B <- 10^4
set.seed(1982)
Ut = runif(B)
head(Ut)
```

```{r}
walk=matrix(rep(NA), nrow = 3, ncol = B)
rownames(walk) = c("x", "y", "z")
x=seq(from = 1, to = B)
colnames(walk) =x
```

```{r}
Xt=c(0, 0 ,0)
for (t in 1:B) {
  if (Ut[t] <= 1/6){
    Xt=Xt+c(1, 0, 0)
    walk[,t]=Xt
  }else if ((Ut[t]>1/6) & (Ut[t] <= 2/6)) {
    Xt=Xt+c(-1, 0, 0)
    walk[,t]=Xt
  }else if ((Ut[t]>2/6) & (Ut[t] <= 3/6)) {
    Xt=Xt+c(0, 1, 0)
    walk[,t]=Xt
  }else if ((Ut[t]>3/6) & (Ut[t] <= 4/6)) {
    Xt=Xt+c(0, -1, 0)
    walk[,t]=Xt
  }else if ((Ut[t]>4/6) & (Ut[t] <= 5/6)) {
    Xt=Xt+c(0, 0, 1)
    walk[,t]=Xt
  }else if (Ut[t]>5/6) {
    Xt=Xt+c(0, 0, -1)
    walk[,t]=Xt
    }
  }
```


```{r}
walk[,B]
```


```{r}
B <- 10^5
set.seed(2000)
Ut = runif(B)
head(Ut)
```

```{r}
walk[,]
```

##segments3D
segments3D (x0, y0, z0, x1 = x0, y1 = y0, z1 = z0, ..., 
         colvar = NULL, phi = 40, theta = 40,
         col = NULL, NAcol = "white", breaks = NULL,
         colkey = NULL, panel.first = NULL,
         clim = NULL, clab = NULL, bty = "b", 
         add = FALSE, plot = TRUE)


